Analyzing Biological Models with the Wasserstein Distance

### 2016-08-18 Paper/Manuscript/Shane's Part/ShaneManuscript.tex
New Data

\begin{equation}
\int_0^{\Delta t} \ dX_t = \sigma \int_{0}^{\Delta t} \ dB_t \implies x_{\Delta t} - x_0 = \sigma \textbf{Z}
\end{equation}
where $\textbf{Z} \sim \mathcal{N}_2(0, \Delta t \mathbb{I}_2)$, where $\mathbb{I}_p$is the $p \times p$ identity matrix. We conclude that
\begin{equation}
x_{\Delta t} = x_0 + \sigma \sqrt{\Delta t}\textbf{W},
\label{eq: BrownianEQ}
\end{equation} 
where $\textbf{W} \sim \mathcal{N}_2(0, \mathbb{I}_2).$ In Figures \ref{fig:macroPlot} and \ref{fig:microPlot} we plot the level curves of the solution to (\ref{eq: Macro2D}) and (\ref{eq: BrownianEQ}) respectively. In Figure \ref{fig: WD}, we plot the WD between Micro and Macro as a function of $t$, where we use $N = 10^3, \Delta t = .01, t = 1, \Delta x = \Delta y = .5.$

\begin{figure}
\begin{subfigure}{.45\linewidth}
\centering
\includegraphics[scale = .45]{MacroPlot.jpg}
\caption{Macro Solution}
\label{fig:macroPlot}
\end{subfigure}%
\begin{subfigure}{.45\linewidth}
\centering
\includegraphics[scale = .45]{MicroPlot.jpg}
\caption{Micro Solution}
\label{fig:microPlot}
\end{subfigure}\\[1ex]
\begin{subfigure}{\linewidth}
\centering
\includegraphics[scale = .45]{WD.jpg}
  \caption{Wasserstein Distance}
\label{fig: WD}
\end{subfigure}
\caption{2D Figures}
\label{fig:test}
\end{figure}

>>>>

\begin{equation}
\int_0^{\Delta t} \ dX_t = \sigma \int_{0}^{\Delta t} \ dB_t \implies x_{\Delta t} - x_0 = \sigma \textbf{Z}
\end{equation}
where $\textbf{Z} \sim \mathcal{N}_2(0, \Delta t \mathbb{I}_2)$, where $\mathbb{I}_p$is the $p \times p$ identity matrix. We conclude that
\begin{equation}
x_{\Delta t} = x_0 + \sigma \sqrt{\Delta t}\textbf{W},
\label{eq: BrownianEQ}
\end{equation} 
where $\textbf{W} \sim \mathcal{N}_2(0, \mathbb{I}_2).$ In Figures \ref{fig:macroPlot} and \ref{fig:microPlot} we plot the level curves of the solution to (\ref{eq: Macro2D}) and (\ref{eq: BrownianEQ}) respectively. We use $N = 10^3, L = M = 5, \Delta x = \Delta y = .2$ at $t = 0,$ where $x \in [-L, L], \ y \in [-M, M]$.
In Figure \ref{fig: WD}, we plot the WD between Micro and Macro as a function of $t$, where we use $N = 10^3,\ \Delta t = .01, \ t = 1, \\ L = M  = 2, \Delta x = \Delta y = .5$

\begin{figure}
\begin{subfigure}{.5\linewidth}
\centering
\includegraphics[scale = .45]{MacroPlot.jpg}
\caption{Macro Solution}
\label{fig:macroPlot}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
\centering
\includegraphics[scale = .45]{MicroPlot.jpg}
\caption{Micro Solution}
\label{fig:microPlot}
\end{subfigure}\\[1ex]
\begin{subfigure}{\linewidth}
\centering
\includegraphics[scale = .45]{WD.jpg}
  \caption{Wasserstein Distance}
\label{fig: WD}
\end{subfigure}
\caption{2D Figures}
\label{fig:test}
\end{figure}
